### 2016-01-25 Irregular-occ/Irregular-occ.tex
Adicionado texto do Josselin

\section{Special tailored Ephemerides (STE) for Jupiter irregular satellites} \label{Sec: integration}

\subsection{Observations used}

The last observations used to develop JPL current ephemeris of the irregular satellites of Jupiter were obtained in 2012 \citep{Jacobson2012}. As a result, the errors in the JPL ephemeris for the current epoch are large enough to prevent accurate predictions of stellar occultations without any corrections. %In order to have efficient ephemerides for predicting the stellar occultations by irregular satellites, we need predictions based on recent observations. This is why we decided to develop our own ephemeris based on the observations published in \cite{GomesJunior2015}.

@@

In order to have efficient ephemerides for predicting the stellar occultations by irregular satellites, we need predictions based on such recent observations. This is why we decided to develop our own
ephemeris based on the observations published in \cite{GomesJunior2015}. First because many of the authors of this paper worked in the production of that set of positions, so that it was very well known. Second, this consistent set of numerous and precise positions covers many orbital periods at many distinct orbital plane sights, so that the orbital inclinations along with all other orbital elements could be satisfactorily derived without the need of further position sets. For these reasons, only this set of recent positions was used for building the new ephemeris for the satellites.

\subsection{Description of the model}

@@

In this work, the STE was used in all but three satellites, not Jovian ones. For these 3 cases, the JPL ephemeris was used instead. The JPL ephemeris for Phoebe is of enough high quality for the short term, mostly thanks to the observations by Cassini. In the case of Triton, the JPL ephemeris is also good enough, as the relatively large diameter of Triton favours the positive detection of occultations. A new short term ephemeris for Nereid is however still needed, but its production was beyond the scope of this work due to its more complicated dynamic, so we used the JPL ephemeris in this case too.

@@

The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the STE ephemeris for Jupiter satellites (see Sec. \ref{Sec: integration}) and JPL ephemeris for the others. The search for stellar candidates follows the same procedure as presented by \cite{Assafin2010, Assafin2012} and \cite{Camargo2014}.

>>>>

\section{Ephemeris} \label{Sec: integration}

%\subsection{Observations used}
In order to have efficient ephemerides for predicting the stellar occultations by irregular satellites, we need predictions based on such recent observations.  This is why we decided to develop our own
ephemeris based on the observations published in \cite{GomesJunior2015}. First because many of the authors of this paper worked in the production of that set of positions, so that it was very well known. Second, this consistent set of numerous and precise positions covers many orbital periods at many distinct orbital plane sights, so that the orbital inclinations along with all other orbital elements could be satisfactorily derived without the need of further position sets. For these reasons, only this set of recent positions was used for building the new ephemeris for the satellites.

@@

%In order to have efficient ephemerides for predicting the stellar occultations by irregular satellites, we need predictions based on such recent observations. This is why we decided to develop our own ephemeris based on the observations published in \cite{GomesJunior2015}. First because many of the authors of this paper worked in the production of that set of positions, so that it was very well known. Second, this consistent set of numerous and precise positions covers many orbital periods at many distinct orbital plane sights, so that the orbital inclinations along with all other orbital elements could be satisfactorily derived without the need of further position sets. For these reasons, only this set of recent positions was used for building the new ephemeris for the satellites.

\subsection{Special tailored Ephemerides (STE) for Jupiter irregular satellites}

The last observations used to develop JPL current ephemeris of the irregular satellites of Jupiter were obtained in 2012 \citep{Jacobson2012}. As a result, the errors in the JPL ephemeris for the current epoch are large enough to prevent accurate predictions of stellar occultations without any corrections.

@@

\subsection{Phoebe's ephemeris}

For the specific case of Phoebe, the ninth satellite of Saturn, we have updated the ephemeris published in \cite{Desmars2013}. The new ephemeris (PH15) used the same dynamical model, including the perturbations of the Sun and the eight planets, the eight major satellites of Saturn and the $J_2$ parameter. The observations used to fit the model are identical to \cite{Desmars2013} (including 223 Cassini observations) with additional observations from \cite{GomesJunior2015}, \cite{Peng2015}, observations from Minor Planet Circulars between 2012 and 2014 (available on the Natural Satellite Data Center at \url{http://lnfm1.sai.msu.ru/neb/nss/bsapoouf.htm}), and observations from Flagstaff \citep{NOFS} between 2012 and 2014. It represents a total number of 5886 observations from 1898 to 2014.

\subsection{Triton's and Nereid's ephemeris}

@@

The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the ephemeris explicited in Sec. \ref{Sec: integration}. The search for stellar candidates follows the same procedure as presented by \cite{Assafin2010, Assafin2012} and \cite{Camargo2014}.
